\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-16 coqimpl.tex
compilation of family STLC
simplify

% \subsection{Language Design}

% \subsection{Plugin Implementation}

>>>>

\input{stlc-compiled.tex}

\begin{itemize}
\item Parameterized by enclosing family "self": explicit extensibility hooks
\item "self" includes only those fields in the context
\item Extensible inductive type $\Rightarrow$ axiomatize
\item Further-bindable \lsti{FRecursion} $\Rightarrow$ axiomatize
\item Non-overridable definitions $\Rightarrow$ expose definitional equality
\item Instantiate inductive types, partial recursors, and equalities $\Rightarrow$ OK to use recursor; equalities easily discharged by \lsti{reflexivity}
\item Instantiate recursion/induction and equalities $\Rightarrow$ OK to use recursor; equalities easily discharged by \lsti{reflexivity}\\
      Code reuse
\end{itemize}

\newpage

### 2022-10-16 stlc-compiled.tex
simplify

\begin{figure}
\begin{minipage}{\textwidth}
\begin{multicols}{2}

\lstset{
  basicstyle=\fontsize{8}{7.8}\ttfamily,
% numbers=left,
}

@@

\newcommand{\innersep}{\vspace{4pt}}
\newcommand{\outersep}{\vspace{4pt}}
\newcommand{\outdent}{\!\!\!}

@@

| tm_unit\_ : tm\_    | tm_var\_ : id -> tm\_
| tm_abs\_  : id -> tm\_ -> tm\_
| tm_app\_  : tm\_ -> tm\_ -> tm\_.

@@

[@\hfill\codecomment{Instantiate \texttt{tm} partial recursor \& equalities}@]
Def tm_prect_STLC P H1 H2 H3 H4 : \forall t, P t :=
  fix F t := match t with
  | tm_unit\_ => H1  | tm_var\_ x => H2 x
  | tm_abs\_ x t => H3 x t (F t)
  | tm_app\_ t1 t2 => H4 t1 (F t1) t2 (F t2) end.
Fact[@\;@][@\textls[-35]{tm\_unit\_eq\_STLC}@][@\,@]:[@\,@][@\dadada@].[@\,@][@\textls[-40]{{\color{dkblue}reflexivity}.}@][@\,@]Qed.[@\hfill@]Fact [@\dadada@][@\tanc{c-STLC-d-tm-end}@][@\innersep@]

@@

[@\hfill\codecomment{Instantiate \texttt{subst} \& equalities}@]
Def subst[@\,@]:[@\,@]tm[@\,@]->[@\,@]id[@\,@]->[@\,@]tm[@\,@]->[@\,@]tm :=[@\tanc{c-STLC-firstcol-end}\columnbreak@]
  tm\__rect _ subst\_tm_unit subst\_tm_var[@\tanc{c-STLC-sndcol-start}@]

@@

Fact[@\;@][@\textls[-40]{subst\_tm\_unit\_eq}@][@\,@]:[@\,@][@\dadada@].[@\,@][@\textls[-40]{{\color{dkblue}reflexivity}.}@][@\,@]Qed.[@\hfill@]Fact [@\dadada@][@\tanc{c-STLC-d-subst-end}@][@\innersep@]
[@\dadada@][@\hfill\codecomment{Instantiate \texttt{ty}, its constructors, partial recusor \& eq.}@][@\tanc{c-STLC-d-ty}@][@\innersep@]

@@

\makeline[0pt]{c-STLC-subst-start}{c-STLC-subst-end}[codecomment-color!50][1.25pt]
\makeline[0pt]{c-STLC-tm-start}{c-STLC-tm-end}[codecomment-color!50][1.25pt]
\makeline[0pt]{c-STLC-ty-start}{c-STLC-ty-end}[codecomment-color!50][1.25pt]
\makeline[0pt]{c-STLC-env-start}{c-STLC-env-end}[codecomment-color!50][1.25pt]
\makeline[0pt]{c-STLC-rest}{c-STLC-rest}[codecomment-color!50][1.25pt]
\makeline[0pt]{c-STLC-start}{c-STLC-firstcol-end}[codecomment-color!50][1.25pt]
\makeline[4pt]{c-STLC-d-tm-start}{c-STLC-d-tm-end}[codecomment-color!25][1.25pt]
\makeline[4pt]{c-STLC-d-subst-start}{c-STLC-firstcol-end}[codecomment-color!20][1.25pt]
\makeline[.5\textwidth+9pt]{c-STLC-sndcol-start}{c-STLC-end}[codecomment-color!50][1.25pt]
\makeline[.5\textwidth+13pt]{c-STLC-sndcol-start}{c-STLC-d-subst-end}[codecomment-color!25][1.25pt]
\makeline[.5\textwidth+13pt]{c-STLC-d-ty}{c-STLC-d-ty}[codecomment-color!25][1.25pt]
\makeline[.5\textwidth+13pt]{c-STLC-d-env}{c-STLC-d-env}[codecomment-color!25][1.25pt]
\makeline[.5\textwidth+13pt]{c-STLC-d-rest}{c-STLC-d-rest}[codecomment-color!25][1.25pt]

\vspace{-15pt}

@@

\begin{lstlisting}
[@\outdent@][@\codecomment{Code emitted upon definition of \texttt{tm} in family \texttt{STLCFix}}@][@\tanc{c-STLCFix-tm-start}@]
[@\outdent@]Module Type STLCFix\_tm\_Ctx.
[@\outdent@]End STLCFix\_tm\_Ctx.[@\innersep@]
[@\outdent@]Module Type STLCFix\_tm (self : STLCFix\_tm\_Ctx).
Include STLC\_tm(self).
Axiom tm_fix : id -> tm -> tm.
Axiom tm_fix_eq_STLC : \forall[@\,@][@\dadada@],[@\,@]tm_prect_STLC [@\dadada@][@\;@]=[@\;@]None.
Axiom tm_prect_STLCFix : [@\dadada@].
Axiom tm_fix_eq_STLCFix : [@\dadada@].
[@\outdent@]End STLCFix\_tm.[@\tanc{c-STLCFix-tm-end}@][@\outersep@]
[@\outdent@][@\codecomment{Code emitted upon definition of \texttt{subst} in family \texttt{STLCFix}}@][@\tanc{c-STLCFix-subst-start}@]
[@\outdent@]Module Type STLCFix\_subst\_Ctx.
Include STLCFix\_tm\_Ctx. Include STLCFix\_tm.
[@\outdent@]End STLCFix\_subst\_Ctx.[@\innersep@]
[@\outdent@]Module STLCFix\_subst\_Cases (self[@\,@]:[@\,@]STLCFix\_subst\_Ctx).
Include STLC\_subst\_Cases(self).
Def subst\_tm_fix := [@\dadada@].
[@\outdent@]End STLCFix\_subst\_Cases.[@\innersep@]
[@\outdent@]Module Type STLCFix\_subst (self[@\,@]:[@\,@]STLCFix\_subst\_Ctx).
Include STLC\_subst(self).
Axiom subst_tm_fix_eq : [@\dadada@].
[@\outdent@]End STLCFix\_subst.[@\tanc{c-STLCFix-subst-end}@][@\outersep@]
[@\outdent@][@\dadada@] [@\codecomment{Code emitted for other fields defined in family \texttt{STLCFix}}@][@\tanc{c-STLCFix-rest}@][@\outersep@]
[@\outdent\codecomment{Code emitted upon completion of family \texttt{STLCFix}}@][@\tanc{c-STLCFix-start}@]
[@\outdent@]Module STLCFix.[@\innersep@]
Inductive tm\_ : Set :=[@\tanc{c-STLCFix-d-tm-start}@]
| tm_unit\_ : tm\_    | tm_var\_ : id -> tm\_
| tm_abs\_  : id -> tm\_ -> tm\_
| tm_app\_  : tm\_ -> tm\_ -> tm\_
| tm_fix\_  : id -> tm\_ -> tm\_.
Def tm := tm\_.[@\hfill\codecomment{Instantiate \texttt{tm} \& its constructors}@]
Def tm_unit := tm_unit\_. Def tm_var := tm_var\_.
Def tm_abs  := tm_abs\_.  Def tm_app := tm_app\_.
Def tm_fix  := tm_fix\_.
[@\dadada@][@\hfill\codecomment{Instantiate \texttt{tm} partial recursors \& equalities}@][@\tanc{c-STLCFix-d-tm-end}@][@\innersep@]
Include STLCFix\_subst\_Cases. [@\tanc{c-STLCFix-d-subst-start}@]
[@\hfill\codecomment{Instantiate \texttt{subst} \& equalities}@]
Def subst[@\,@]:[@\,@]tm[@\,@]->[@\,@]id[@\,@]->[@\,@]tm[@\,@]->[@\,@]tm :=
  tm\__rect _ subst\_tm_unit subst\_tm_var
             subst\_tm_abs  subst\_tm_app subst\_tm_fix.
Fact[@\;@][@\textls[-40]{subst\_tm\_unit\_eq}@][@\,@]:[@\,@][@\dadada@].[@\,@][@\textls[-40]{{\color{dkblue}reflexivity}.}@][@\,@]Qed.[@\hfill@]Fact [@\dadada@][@\tanc{c-STLCFix-d-subst-end}@][@\innersep@]
[@\dadada@][@\hfill\codecomment{\textls[-10]{Instantiate \texttt{ty}, its constructors, partial recursor \& eq.}}@][@\tanc{c-STLCFix-d-ty}@][@\innersep@]
Include STLC\_env.[@\hfill\codecomment{Include \texttt{env}}@][@\tanc{c-STLCFix-d-env}@][@\innersep@]
[@\dadada@][@\hfill\codecomment{Include/Instantiate other fields of family \texttt{STLCFix}}@][@\tanc{c-STLCFix-d-rest}@][@\innersep@]
[@\outdent@]End STLCFix.[@\tanc{c-STLCFix-end}@]
\end{lstlisting}

\makeline[.5\textwidth+9pt]{c-STLCFix-tm-start}{c-STLCFix-tm-end}[codecomment-color!50][1.25pt]
\makeline[.5\textwidth+9pt]{c-STLCFix-subst-start}{c-STLCFix-subst-end}[codecomment-color!50][1.25pt]
\makeline[.5\textwidth+9pt]{c-STLCFix-rest}{c-STLCFix-rest}[codecomment-color!50][1.25pt]
\makeline[.5\textwidth+9pt]{c-STLCFix-start}{c-STLCFix-end}[codecomment-color!50][1.25pt]
\makeline[.5\textwidth+13pt]{c-STLCFix-d-tm-start}{c-STLCFix-d-tm-end}[codecomment-color!25][1.25pt]
\makeline[.5\textwidth+13pt]{c-STLCFix-d-subst-start}{c-STLCFix-d-subst-end}[codecomment-color!25][1.25pt]
\makeline[.5\textwidth+13pt]{c-STLCFix-d-ty}{c-STLCFix-d-ty}[codecomment-color!25][1.25pt]
\makeline[.5\textwidth+13pt]{c-STLCFix-d-env}{c-STLCFix-d-env}[codecomment-color!25][1.25pt]
\makeline[.5\textwidth+13pt]{c-STLCFix-d-rest}{c-STLCFix-d-rest}[codecomment-color!25][1.25pt]

\vspace{-15pt}

@@

\begin{lstlisting}
[@\outdent@][@\codecomment{Code emitted upon command \texttt{Check} \dadada}@][@\tanc{c-Check-STLCFix-typesafe-start}@]
[@\outdent@]Check STLCFix.typesafe.[@\tanc{c-Check-STLCFix-typesafe-end}@]
\end{lstlisting}

\makeline[.5\textwidth+9pt]{c-Check-STLCFix-typesafe-start}{c-Check-STLCFix-typesafe-end}[codecomment-color!35][1.25pt]

@@

\vspace{-8pt}

>>>>

\begin{figure}
\vspace{-5pt}
\begin{minipage}{\textwidth}
\begin{multicols}{2}

\lstset{
  basicstyle=\fontsize{8}{8.2}\ttfamily,
% numbers=left,
}

@@

\newcommand{\innersep}{\vspace{6pt}}
\newcommand{\outersep}{\vspace{5pt}}
\newcommand{\outdent}{\!\!\!}

@@

| tm_unit\_[@\,@]:[@\,@]tm\_ | tm_var\_[@\,@]:[@\,@]id -> tm\_
| tm_abs\_[@\,@]:[@\,@]id->tm\_->tm\_ | tm_app\_[@\,@]:[@\,@]tm\_->tm\_->tm\_.

@@

[@\hfill\codecomment{Instantiate \texttt{tm} partial recursor \& its equalities}@]
Def tm_prect_STLC P := tm\__rect (\lambda[@\,@]t,[@\,@]option[@\,@](P[@\,@]t)).
Fact[@\;@][@\textls[-20]{tm\_unit\_eq\_STLC}@][@\,@]:[@\,@][@\dadada@].[@\,@][@\textls[-40]{{\color{dkblue}reflexivity}.}@][@\,@]Qed.[@\hfill@]Fact [@\dadada@][@\tanc{c-STLC-d-tm-end}@][@\innersep@]

@@

Def subst[@\,@] :=[@\hfill\codecomment{Instantiate \texttt{subst} \& its equalities}@]
  tm\__rect _ subst\_tm_unit subst\_tm_var

@@

Fact[@\;@][@\textls[-40]{subst\_tm\_unit\_eq}@][@\,@]:[@\,@][@\dadada@].[@\,@][@\textls[-40]{{\color{dkblue}reflexivity}.}@][@\,@]Qed.[@\hfill@]Fact [@\dadada@][@\tanc{c-STLC-d-subst-end}@][@\tanc{c-STLC-firstcol-end}\columnbreak@][@\innersep@]
[@\dadada@][@\hfill\codecomment{Instantiate \texttt{ty}, its constructors, partial recusor \& eq.}@][@\tanc{c-STLC-d-ty}@][@\tanc{c-STLC-sndcol-start}@][@\innersep@]

@@

\makeline[-1pt]{c-STLC-subst-start}{c-STLC-subst-end}[codecomment-color!55][1.8pt]
\makeline[-1pt]{c-STLC-tm-start}{c-STLC-tm-end}[codecomment-color!55][1.8pt]
\makeline[-1pt]{c-STLC-ty-start}{c-STLC-ty-end}[codecomment-color!55][1.8pt]
\makeline[-1pt]{c-STLC-env-start}{c-STLC-env-end}[codecomment-color!55][1.8pt]
\makeline[-1pt]{c-STLC-rest}{c-STLC-rest}[codecomment-color!55][1.8pt]
\makeline[-1pt]{c-STLC-start}{c-STLC-firstcol-end}[codecomment-color!55][1.8pt]
\makeline[4pt]{c-STLC-d-tm-start}{c-STLC-d-tm-end}[codecomment-color!35][1.0pt]
\makeline[4pt]{c-STLC-d-subst-start}{c-STLC-firstcol-end}[codecomment-color!35][1.0pt]
\makeline[.5\textwidth+8pt]{c-STLC-sndcol-start}{c-STLC-end}[codecomment-color!55][1.8pt]
\makeline[.5\textwidth+12pt]{c-STLC-d-ty}{c-STLC-d-ty}[codecomment-color!35][1.0pt]
\makeline[.5\textwidth+12pt]{c-STLC-d-env}{c-STLC-d-env}[codecomment-color!35][1.0pt]
\makeline[.5\textwidth+12pt]{c-STLC-d-rest}{c-STLC-d-rest}[codecomment-color!35][1.0pt]

\vspace{-12pt}

@@

\begin{lstlisting}
[@\outdent@][@\codecomment{Code emitted upon definition of \texttt{tm} in family \texttt{STLCFix}}@][@\tanc{c-STLCFix-tm-start}@]
[@\outdent@]Module Type STLCFix\_tm\_Ctx.
[@\outdent@]End STLCFix\_tm\_Ctx.[@\innersep@]
[@\outdent@]Module Type STLCFix\_tm (self : STLCFix\_tm\_Ctx).
Include STLC\_tm(self).
Axiom tm_fix : id -> tm -> tm.
Axiom tm_fix_eq_STLC : \forall[@\,@][@\dadada@],[@\,@]tm_prect_STLC [@\dadada@][@\;@]=[@\;@]None.
Axiom tm_prect_STLCFix : [@\dadada@].
Axiom tm_fix_eq_STLCFix : [@\dadada@].
[@\outdent@]End STLCFix\_tm.[@\tanc{c-STLCFix-tm-end}@][@\outersep@]
[@\outdent@][@\codecomment{Code emitted upon definition of \texttt{subst} in family \texttt{STLCFix}}@][@\tanc{c-STLCFix-subst-start}@]
[@\outdent@]Module Type STLCFix\_subst\_Ctx.
Include STLCFix\_tm\_Ctx. Include STLCFix\_tm.
[@\outdent@]End STLCFix\_subst\_Ctx.[@\innersep@]
[@\outdent@]Module STLCFix\_subst\_Cases (self[@\,@]:[@\,@]STLCFix\_subst\_Ctx).
Include STLC\_subst\_Cases(self).
Def subst\_tm_fix := [@\dadada@].
[@\outdent@]End STLCFix\_subst\_Cases.[@\innersep@]
[@\outdent@]Module Type STLCFix\_subst (self[@\,@]:[@\,@]STLCFix\_subst\_Ctx).
Include STLC\_subst(self).
Axiom subst_tm_fix_eq : [@\dadada@].
[@\outdent@]End STLCFix\_subst.[@\tanc{c-STLCFix-subst-end}@][@\outersep@]
[@\outdent@][@\dadada@] [@\codecomment{Code emitted for other fields defined in family \texttt{STLCFix}}@][@\tanc{c-STLCFix-rest}@][@\outersep@]
[@\outdent\codecomment{Code emitted upon completion of family \texttt{STLCFix}}@][@\tanc{c-STLCFix-start}@]
[@\outdent@]Module STLCFix.[@\innersep@]
Inductive tm\_ : Set :=[@\tanc{c-STLCFix-d-tm-start}@]
| tm_unit\_[@\,@]:[@\,@]tm\_ | tm_var\_[@\,@]:[@\,@]id -> tm\_
| tm_abs\_[@\,@]:[@\,@]id->tm\_->tm\_ | tm_app\_[@\,@]:[@\,@]tm\_->tm\_->tm\_
| tm_fix\_[@\,@]:[@\,@]id->tm\_->tm\_.
Def tm := tm\_.[@\hfill\codecomment{Instantiate \texttt{tm} \& its constructors}@]
Def tm_unit := tm_unit\_. Def tm_var := tm_var\_.
Def tm_abs  := tm_abs\_.  Def tm_app := tm_app\_.
Def tm_fix  := tm_fix\_.
[@\dadada@][@\hfill\codecomment{Instantiate \texttt{tm} partial recursors \& their equalities}@][@\tanc{c-STLCFix-d-tm-end}@][@\innersep@]
Include STLCFix\_subst\_Cases. [@\tanc{c-STLCFix-d-subst-start}@]
Def subst :=[@\hfill\codecomment{Instantiate \texttt{subst} \& its equalities}@]
  tm\__rect _ subst\_tm_unit subst\_tm_var
             subst\_tm_abs  subst\_tm_app subst\_tm_fix.
Fact[@\;@][@\textls[-40]{subst\_tm\_unit\_eq}@][@\,@]:[@\,@][@\dadada@].[@\,@][@\textls[-40]{{\color{dkblue}reflexivity}.}@][@\,@]Qed.[@\hfill@]Fact [@\dadada@][@\tanc{c-STLCFix-d-subst-end}@][@\innersep@]
[@\dadada@][@\hfill\codecomment{\textls[-10]{Instantiate \texttt{ty}, its constructors, partial recursor \& eq.}}@][@\tanc{c-STLCFix-d-ty}@][@\innersep@]
Include STLC\_env.[@\hfill\codecomment{Include \texttt{env}}@][@\tanc{c-STLCFix-d-env}@][@\innersep@]
[@\dadada@][@\hfill\codecomment{Include/Instantiate other fields of family \texttt{STLCFix}}@][@\tanc{c-STLCFix-d-rest}@][@\innersep@]
[@\outdent@]End STLCFix.[@\tanc{c-STLCFix-end}@]
\end{lstlisting}

\makeline[.5\textwidth+8pt]{c-STLCFix-tm-start}{c-STLCFix-tm-end}[codecomment-color!55][1.8pt]
\makeline[.5\textwidth+8pt]{c-STLCFix-subst-start}{c-STLCFix-subst-end}[codecomment-color!55][1.8pt]
\makeline[.5\textwidth+8pt]{c-STLCFix-rest}{c-STLCFix-rest}[codecomment-color!55][1.8pt]
\makeline[.5\textwidth+8pt]{c-STLCFix-start}{c-STLCFix-end}[codecomment-color!55][1.8pt]
\makeline[.5\textwidth+13pt]{c-STLCFix-d-tm-start}{c-STLCFix-d-tm-end}[codecomment-color!35][1.0pt]
\makeline[.5\textwidth+13pt]{c-STLCFix-d-subst-start}{c-STLCFix-d-subst-end}[codecomment-color!35][1.0pt]
\makeline[.5\textwidth+13pt]{c-STLCFix-d-ty}{c-STLCFix-d-ty}[codecomment-color!35][1.0pt]
\makeline[.5\textwidth+13pt]{c-STLCFix-d-env}{c-STLCFix-d-env}[codecomment-color!35][1.0pt]
\makeline[.5\textwidth+13pt]{c-STLCFix-d-rest}{c-STLCFix-d-rest}[codecomment-color!35][1.0pt]

\vspace{-12pt}

@@

\begin{lstlisting}
[@\outdent@][@\codecomment{Code emitted upon command \texttt{\textls[-35]{Check STLCFix.typesafe}}}@][@\tanc{c-Check-STLCFix-typesafe-start}@]
[@\outdent@]Check STLCFix.typesafe.[@\tanc{c-Check-STLCFix-typesafe-end}@]
\end{lstlisting}

\makeline[.5\textwidth+8pt]{c-Check-STLCFix-typesafe-start}{c-Check-STLCFix-typesafe-end}[codecomment-color!50][1.8pt]

@@

%\vspace{-10pt}
